---
title: "Getting Started with the SimpLin Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with the SimpLin Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, setup}
library(SimpLin)
```


To illustrate how to use this package, we will use the `mtcars` which does not require the installation of a package. We will regress miles per gallon (mpg) on weight (wt). 

```{r, comment = NA}
regress_list <- SimpLinR(x = mtcars$wt, y = mtcars$mpg)
```

To get the vector of estimated regression coefficients run this line of code. 

```{r, comment = NA}
regress_list[["coefficients"]]
```
The first entry corresponds to the estimate of the intercept term and the second entry corresponds to the estimate of the slope term. i.e. -5.344472 is our estimate for $\hat{\beta}_1$. 

Here is how you access $SE(\hat{\beta_0}). 
```{r, comment = NA}
regress_list[["SE B0"]]
```

Here is how you access $SE(\hat{\beta_0}). 

```{r, comment = NA}
regress_list[["SE B0"]]
```

Here is how you access $SE(\hat{\beta_1}). 

```{r, comment = NA}
regress_list[["SE B1"]]
```

Here is the 95% confidence interval for $\hat{\beta_0}$. 

```{r, comment = NA}
regress_list[["95% CI B0"]]
```

Here is the 95% confidence interval for $\hat{\beta_1}$. 

```{r, comment = NA}
regress_list[["95% CI B1"]]
```

Here is a vector of the first 5 predicted values. 

```{r, comment = NA}
head(regress_list[["y hat"]], 5)
```
Here is the first 5 entries from the vector of residuals. If you want all teh residuals, or predicted values, just don't use the head function. 

```{r, comment = NA}
head(regress_list[["residuals"]], 5)
```

